Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-07-12 snapshot_system/con.tex
Revisions to evaluation section

\section{Conclusion}
\label{sect:final}
In this paper we propose a VM-centric deduplication scheme for 
VM snapshot backup in the cloud for maximizing fault isolation and tolerance. 
Inner-VM deduplication localizes backup data dependency and exposes more parallelism  
while cross-VM deduplication with a small common data set
effectively  covers a large percent of duplicate data.
The scheme organizes the write of small data chunks into large file system blocks so
that each underlying file block is associated with one VM for most cases.
by keeping most of the VM-FSB mappings 1:1 we isolate faults and improve overal fault tolerance.
Our solution accomplishes reasonable and competitive deduplication efficiency while
still meeting stringent cloud resource usage requirements. 
Our analysis shows that  this VM centric scheme 
can  provide  better fault tolerance that VM-oblivious global deduplication schemes
while using a small amount of computing and storage resource.

>>>>

\section{Conclusion}
\label{sect:final}
In this paper we propose a VM-centric deduplication scheme for 
VM snapshot backup in the cloud for maximizing fault isolation and tolerance. 
Inner-VM deduplication localizes backup data dependency and exposes more parallelism  
while cross-VM deduplication with a small common data set
effectively  covers a large percent of duplicate data.
The scheme organizes the write of small data chunks into large file system blocks so
that each underlying file block is associated with one VM for most cases.
by keeping most of the FSBs only referenced by 1 VM, we isolate faults and improve overal fault tolerance.
Our solution accomplishes reasonable and competitive deduplication efficiency while
still meeting stringent cloud resource usage requirements. 
Our analysis shows that  this VM centric scheme 
can  provide  better fault tolerance than VM-oblivious global deduplication schemes
while using a small amount of computing and storage resources.

### 2013-07-12 snapshot_system/eval1.tex
Revisions to evaluation section

We have implemented and evaluated a prototype of our VO scheme on a Linux cluster
of 8-core AMD FX-8120 at 3.1 GHz with 16 GB RAM. 
Our implementation is based on Alibaba's Xen cloud platform~\cite{Aliyun,WeiZhangIEEE}.
Each machine  is equipped with a 
a distributed file system (QFS) running in the cluster manages six 3TB disks
with default replication degree set to 3. The PDS replication is set to 5.
Objectives of our evaluation are:
1) Study the deduplicate detection and removal effectiveness of the VC approach and compare with an alternative VO
design.
2) Examine the impacts of VC for fault isolation and tolerance. 
3) Evaluate the backup throughput performance VC  for a large number of VMs.
4) Assess the resource usage  of VC in terms of memory, storage, and network bandwidth.
% the backup throughput performance VC  for a large number of VMs.
%Compare with the data domain approach~\cite{bottleneck08}.

@@

We will also compare our VC approach with  with
a VO approach  using stateless routing with binning (SRB).
SRB executes a distributed deduplication by routeing a data chunk to a machine~\cite{ParallelDataDomain}
using  the chunk hashing function discussed in \cite{??}. Within such a machine, the data chunk is compared with
a local index.

\comments{
%We are running our deduplication/backup  service on 100 nodes.
%Memory usage is about 150MB space per node during backup and
%the CPU usage is very small during the experiments. 
We have performed a trace-driven study using  a 1323 VM dataset  collected from 
%100 Alibaba Aliyun's cloud nodes~\cite{WeiZhangIEEE}.
a cloud cluster at Alibaba's Aliyun.
 ~\cite{WeiZhangIEEE}.
% and each of machine nodes has 16 cores and 12 disk drives,  hosting  up to 25 VMs. 
For each VM, the system keeps 10 automatically-backed snapshots in the storage while
a user may instruct extra snapshots to be saved.
Each VMs uses   one of the most popular 7 OSes: 
Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. 
The backup of VM snapshots is completed within a few  hours every night.
Based on our study of production  data,  each VM has about  40GB of storage  data on average
including OS and user data disk.
Each VM image is  divided into 2 MB fix-sized segments and each segment is divided into 
variable-sized content blocks  with an average size of 4KB.
%variable sizes~\cite{similar94,rabin81} with an average size of 4KB. 
The signature for variable-sized blocks is computed using their SHA-1 hash.

The seek cost of each random IO request in our test machines is about  10 milliseconds.
The average I/O usage of local storage is controlled about 50MB/second for backup 
in the presence of other I/O jobs. Noted that a typical 1U server can host
6 to 8  hard drives and deliver over 300MB/second. Our setting uses 16.7\% or less 
of local storage bandwidth. 
The final snapshots are stored in a distributed file system built on the same 
cluster. total local disk usage on each machine is about 8GB for the duplicate detection purpose,
mainly for global index. 
Level 1 segment dirty bits identify 78\% of duplicate blocks. For the remaining dirty segments,
block-wise full deduplication removes about additional 74.5\% of duplicates.
The final content copied to the backup storage is reduced by 94.4\% in total.
}
%\begin{figure}
%\centering
%\includegraphics[width=0.4\textwidth]{mem_time}
%\caption{ Parallel time when memory limit varies.}
%\label{fig:memory}
%%\end{figure}
%
%Figure~\ref{fig:memory} shows the total parallel time in hours to backup 2500 VMs on
% a 100-node cluster a  when

\subsection{Settings}
We have performed a trace-driven study using  a 1323 VM dataset  collected from 
100 Alibaba Aliyun's cloud nodes~\cite{WeiZhangIEEE}.
The production environment tested has  about 1000 machines with 25 VMs on each machine.
%We are running our deduplication/backup  service on 100 nodes.
%Memory usage is about 150MB space per node during backup and
%the CPU usage is very small during the experiments. 
% and each of machine nodes has 16 cores and 12 disk drives,  hosting  up to 25 VMs. 
For each VM, the system keeps 10 automatically-backed snapshots in the storage while
a user may instruct extra snapshots to be saved.
%Each VM uses   one of the most popular 7 OSes: 
%Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. 
The backup of VM snapshots is completed within a few  hours every night.
Based on our study of production  data,  each VM has about  40GB of storage  data  on average
including OS and user data disk.
All data are divided into 2 MB fix-sized segments and each segment is divided into 
variable-sized content chunks ~\cite{similar94,rabin81} with an average size of 4KB.
The signature for variable-sized blocks is computed using their SHA-1 hash. 
Popularity of data blocks are collected through global counting 
and the top 1\% will fall into PDS, as discussed in Section~\ref{sect:crossVM}.
%variable sizes~\cite{similar94,rabin81} with an average size of 4KB. 
%The signature for variable-sized blocks is computed using their SHA-1 hash.

@@

Since it's impossible to perform large scale analysis without affecting the VM performance,
we sampled two data sets from real user VMs to measure the effectiveness of our deduplication scheme.
Dataset1 is used study the detail impact of 3-level deduplication process,
it compose of 35 VMs from 7 popular OSes: 
Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. For each OS, 
5 VMs are chosen, and every VM come with 10 full snapshots of it OS and data disk. 
The overall data size for this 700 full snapshots is 17.6 TB.

@@

Figure~\ref{fig:exbin-efficiency-graph} shows the deduplication efficiency for SRB and VC.
We define deduplication efficiency to be the percent of duplicate chunks
which are detected and deduplicated.
The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' means that
we allocate the space of distributed shared memory  to accommodate 2\%
of data chunks shared among VMs, as defined in Table~\ref{tab:symbol}. Namely 
With $\sigma=2\%$, the deduplication efficiency can reach over 90\% 
while with $\sigma=4\%$, the deduplication efficiency can reach over 92\%. 
The loss of efficiency in VC is caused by the restriction of the total physical memory available
in the cluster to support the PDS.  
The loss of efficiency in SRB is caused by the routing of data chunks which restricts the search scope
for global comparison.
In all cases, VC provides similar or better deduplication efficiency than SRB.

@@

Figure~\ref{fig:srb_vs_vc} shows
the  average  processing  time of  each segment using VC and SRM in handling our dataset.
It has a breakdown of time for reading data and updating the metadata, network latency to visit
a remote machine, and index access for finger printer comparison.
SRB has a higher index access and fingerprint comparison because once a chunk is routed to a machine,
it relies on this local machine to access its index (often on the disk) and perform comparison.
VC is faster for index access because it conducts in-memory local search first and then
accesses  the PDS which is on distributed shared memory.  
SRB spends  slighter more time in  reading data and update because it also updates the on-disk
local meta data index.
Overall speaking,  VC is faster than SRB while data reading dominates the processing time. 
%all lookups are essentially random and caching will be largely innefective).

@@

Figure~\ref{fig:single_vm_backup} reports the average bacup time for a VM with VC with a varying number
of PDS size.
Again it shows that data reading dominates the backup process, our deduplication
procedure only takes a small fraction of the total backup time. 
The change of $\delta$ does not significantly affects the overall time and
PDS lookup takes a small amount of time.
%Larger memory permits us to
%use larger PDS index to cover more of global index, as a result the amount of data to be writen
%is reduced and so do the writing time.
%Inside the deduplication procedure, the time costs of level-1
%is plainly zero, and the costs of level-2 and level-3 are almost identical under different settings
%because the number of fingerprints to process are just the same.

@@

    Figure~\ref{fig:parallel_backup} shows the node throughput when all machine nodes run
the backup procedure in parallel.
To begin, on each node we let 4 VMs writing snapshot concurrently, and gradually 
increase number of VMs to 12 to saturate our system capability. We observed 
the per-node throughput peaked at 2700 MB/s when writing 10 VM snapshots in parallel, 
which is far beyond our QFS file system capability. The reason behind it is our efficient
deduplication architecture and compression greatly reduce the amount of data that need to be written to
the file system. The main bottleneck here is our QFS only manages one disk per node, 
making it inefficient to utilize the benefits of parallel disk access. We expect our architecture can
perform even better in production clusters which often have more than ten disks on each node.

>>>>

We have implemented and evaluated a prototype of our VC scheme on a Linux cluster of machines with
8-core AMD FX-8120 at 3.1 GHz with 16 GB RAM. 
Our implementation is based on Alibaba's Xen cloud platform~\cite{Aliyun,WeiZhangIEEE}.
Each machine  is equipped with a 
a distributed file system (QFS) and overall the cluster manages six 3TB disks
with default replication degree set to 3. The PDS replication is set to 5.
Objectives of our evaluation are:
1) Study the duplicate detection and removal effectiveness of the VC approach and compare with an alternative VO
design.
2) Examine the impacts of VC for fault isolation and tolerance. 
3) Evaluate the backup throughput performance VC  for a large number of VMs.
4) Assess the resource usage  of VC in terms of memory, storage, and network bandwidth.
% the backup throughput performance VC  for a large number of VMs.
%Compare with the data domain approach~\cite{bottleneck08}.

@@

We will also compare our VC approach with  with
a VO approach  using stateless routing with binning (SRB).
SRB executes a distributed deduplication by routing a data chunk to a machine~\cite{ParallelDataDomain}
using  the chunk hashing function discussed in \cite{??}. Within such a machine,
the data chunk is compared with a local index. This minHash paritioning
algorithm helps provide a greater degree of parallelism, but ignores the
significant amount of parallelism within a single VM.

\comments{
%We are running our deduplication/backup  service on 100 nodes.
%Memory usage is about 150MB space per node during backup and
%the CPU usage is very small during the experiments. 
We have performed a trace-driven study using  a 1323 VM dataset  collected from 
%100 Alibaba Aliyun's cloud nodes~\cite{WeiZhangIEEE}.
a cloud cluster at Alibaba's Aliyun.
 ~\cite{WeiZhangIEEE}.
% and each of machine nodes has 16 cores and 12 disk drives,  hosting  up to 25 VMs. 
For each VM, the system keeps 10 automatically-backed snapshots in the storage while
a user may instruct extra snapshots to be saved.
Each VMs uses   one of the most popular 7 OSes: 
Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. 
The backup of VM snapshots is completed within a few  hours every night.
Based on our study of production  data,  each VM has about  40GB of storage  data on average
including OS and user data disk.
For our system each VM image is  divided into 2 MB fix-sized segments and each segment is divided into 
variable-sized content blocks  with an average size of 4KB.
%variable sizes~\cite{similar94,rabin81} with an average size of 4KB. 
The signature for variable-sized blocks is computed using their SHA-1 hash.

The seek cost of each random IO request in our test machines is about  10 milliseconds.
The average I/O usage of local storage is controlled to about 50MB/second for backup 
in the presence of other I/O jobs. Noted that a typical 1U server can host
6 to 8  hard drives and deliver over 300MB/second. Our setting uses 16.7\% or less 
of local storage bandwidth. 
The final snapshots are stored in a distributed file system built on the same 
cluster. total local disk usage on each machine is about 8GB for the duplicate detection purpose,
mainly for global index. 
Level 1 segment dirty bits identify 78\% of duplicate blocks. For the remaining dirty segments,
block-wise full deduplication removes about additional 74.5\% of duplicates.
The final content copied to the backup storage is reduced by 94.4\%
\emph{Is this correct? Elsewhere we have used 92\% based on results from
our srb-vc comparison graph} in total.
}
%\begin{figure}
%\centering
%\includegraphics[width=0.4\textwidth]{mem_time}
%\caption{ Parallel time when memory limit varies.}
%\label{fig:memory}
%%\end{figure}
%
%Figure~\ref{fig:memory} shows the total parallel time in hours to backup 2500 VMs on
% a 100-node cluster a  when

\subsection{Settings}
We have performed a trace-driven study using  a 1323 VM dataset  collected from 
100 Alibaba Aliyun's cloud nodes~\cite{WeiZhangIEEE}.
The production environment tested has  about 1000 machines with 25 VMs on each machine.
%We are running our deduplication/backup  service on 100 nodes.
%Memory usage is about 150MB space per node during backup and
%the CPU usage is very small during the experiments. 
% and each of machine nodes has 16 cores and 12 disk drives,  hosting  up to 25 VMs. 
For each VM, the system keeps 10 automatically-backed snapshots in the storage while
a user may instruct extra snapshots to be saved.
%Each VM uses   one of the most popular 7 OSes: 
%Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. 
The backup of VM snapshots is completed within a few  hours every night.
Based on our study of production  data,  each VM has about  40GB of storage  data  on average
including OS and user data disk.
All data are divided into 2 MB fix-sized segments and each segment is divided into 
variable-sized content chunks ~\cite{similar94,rabin81} with an average size of 4KB.
The signature for variable-sized blocks is computed using their SHA-1 hash. 
Popularity of data blocks are collected through global counting 
and the top 1-2\% will fall into the PDS, as discussed in Section~\ref{sect:crossVM}.
%variable sizes~\cite{similar94,rabin81} with an average size of 4KB. 
%The signature for variable-sized blocks is computed using their SHA-1 hash.

@@

Since it's impossible to perform large scale analysis without affecting production VM performance,
we sampled two data sets from real user VMs to measure the effectiveness of our deduplication scheme.
Dataset1 is used study the detail impact of 3-level deduplication process,
it compose of 35 VMs from 7 popular OSes: 
Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. For each OS, 
5 VMs are chosen, and every VM come with 10 full snapshots of it OS and data disk. 
The overall data size for these 700 full snapshots is 17.6 TB.

@@

Figure~\ref{fig:exbin-efficiency-graph} shows the deduplication efficiency for SRB and VC.
We define deduplication efficiency to be the percent of duplicate chunks
which are detected and deduplicated.
The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' means that
we allocate the space of distributed shared memory  to accommodate 2\%
of data chunks shared among VMs, as defined in Table~\ref{tab:symbol}. Namely 
With $\sigma=2\%$, the deduplication efficiency can reach over 90\% 
while with $\sigma=4\%$, the deduplication efficiency can reach 92\%. 
The loss of efficiency in VC is caused by the restriction of the total physical memory available
in the cluster to support the PDS.  
The loss of efficiency in SRB is caused by the routing of data chunks which restricts the search scope
for global comparison.
In all cases, VC provides similar or better deduplication efficiency than SRB.

@@

Figure~\ref{fig:srb_vs_vc} shows
the  average  processing  time of  each segment using VC and SRM in handling our dataset.
It has a breakdown of time for reading data and updating the metadata, network latency to visit
a remote machine, and index access for finger printer comparison.
SRB has a higher index access and fingerprint comparison because once a chunk is routed to a machine,
it relies on this local machine to access its index (often on the disk) and perform comparison.
VC is faster for index access because it conducts in-memory local search first and then
accesses  the PDS which is on distributed shared memory.  
SRB spends  slighter more time in  reading data and updates because it also updates the on-disk
local meta data index.
Overall,  VC is faster than SRB, though data reading dominates the processing time for both algorithms.
%all lookups are essentially random and caching will be largely innefective).

@@

Figure~\ref{fig:single_vm_backup} reports the average bacup time for a VM in VC with a varying PDS size.
Again it shows that data reading dominates the backup process; our deduplication
procedure only takes a small fraction of the total backup time. 
The change of $\sigma$ does not significantly affect the overall backup speed as
PDS lookup takes only a small amount of time.
%Larger memory permits us to
%use larger PDS index to cover more of global index, as a result the amount of data to be writen
%is reduced and so do the writing time.
%Inside the deduplication procedure, the time costs of level-1
%is plainly zero, and the costs of level-2 and level-3 are almost identical under different settings
%because the number of fingerprints to process are just the same.

@@

    Figure~\ref{fig:parallel_backup} shows the node throughput when all machine nodes run
the backup procedure in parallel.
To begin, on each node we write snapshots for 4 VMs concurrently, and gradually 
increase number of VMs to 12 to saturate our system capability. We observed 
the per-node throughput peaked at 2700 MB/s when writing 10 VM snapshots in parallel, 
which is far beyond our QFS file system capability. The reason behind it is our efficient
deduplication architecture and compression which greatly reduce the amount of data that needs to be written to
the file system. The main bottleneck here is that our QFS installation only
manages one disk per node, which prevents it from fully utilizing the the
benefits of parallel disk access. We expect our architecture can
perform even better in production clusters, which often have ten or more disks on each node.
